Deterministic and statistical truncated KdV models for anomalous waves induced by abrupt depth change

### 2018-09-27 LatexNotes/Notes.tex
NM

@@

@@

\newpage
\newpage
\section{Experimental parameters}

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{Some relevant experimental parameters} 
\vspace{0.3 pc}
\begin{tabular}{c l l}
\hline
\hspace{0.5pc} Symbol
\hspace{0.5pc} & Meaning 
\hspace{0.5pc} & Value \\
\hline
N/A		& Length of the experimental tank (in wave direction)	& 6 m	\\
$L_0$	& Width of the experimental tank	 (transverse)		& $L_0 = $ 20 cm	\\
$f_0$	& Dominant forcing frequency in experiments	& $f_0 = $ 2 Hz	\\
$\hm$	& Depth on deep side						& $\hm = 12.5$ cm \\
$\hp$	& Depth on shallow side					& $\hp = 3$ cm \\
$\lamm$	& Wavelength induced by 2 Hz forcing on deep side	& $\lamm = 38$ cm	\\
$\lamp$	& Wavelength induced by 2 Hz forcing on shallow side	& $\lamp = 25$ cm	\\
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

\begin{comment}
% Majda's notes typed up
\section{Deterministic model for waves over abrupt depth change}

The surface-displacement is denoted $u(x,t)$.

Modeling assumptions
\begin{enumerate}
\item Waves in a narrow channel (width $L_0$) are nearly unidirectional and $2 \pi L_0$ periodic (purely a mathematical idealization, not realistic I believe). Where $L_0 < \lambda$, with $\lambda$ a characteristic wavelength. As seen in the table, this later assumption is reasonable since $L_0 / \lamm \approx 0.5$
\item The role of the paddle forcing is to generate a state with `zero momentum', $M = \intt u \, dx = 0$ (this assumption is strongly supported by experimental measurements pointwise!) and with some given energy $E_0 = \frac{1}{2} \intt u^2 \, dx$ (not an assumption, just a statement). Here, $E_0$ is a function of the strength of the paddle forcing.
\item Assume a Galerkin truncation of $u(x,t) \approx u_{\Lambda}(x,t)$, where $\Lambda$ (fixed) will probably be 20 or 30.
\item The `time' coordinate $t$  corresponds physically to a downstream spatial coordinate (i.e.~$X \approx \eps x$ in Johnson's notation). The abrupt depth change (ADC) corresponds to $t = t_0$ or $T_{ADC}$.
\end{enumerate}
\end{comment}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Experimental Preliminaries
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental parameters}

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{Basic experimental parameters and scales.}
\label{paramtable}
\begin{tabular}{l l l}
\hline Parameter & Upstream  value \,\, & Downstream value \\
\hline
peak forcing frequency			& 2 Hz			& N/A \\
depth, $h$						& 12.5 cm			& 3 cm \\
peak wavelength, $\lambda_p$		& 38 cm			& 25 cm \\
peak wavenumber, $k_p$			& 0.17 rad/cm		& 0.25 rad/cm \\
dimensionless depth, $k_p h$\,\,\,		& 2.1			& 0.76 \\
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

@@

\subsubsection{Non-dimensionalization}

The KdV equation in dimensional form is
\begin{equation}
2 \eta_t + \frac{3 c}{h_0} \eta \eta_{\xi} + \frac{c h_0^2}{3} \eta_{\xi \xi \xi} = 0
\end{equation}
Here, $\eta$ has units of length, $t$ time, $c = \sqrt{g h_0}$ is the wave speed, and $\xi = x - ct$. I obtained this equation by starting from Johnson's dimensionless equation ()

@@
